### 2019-02-25 manuscript.tex
Update manuscript.tex

There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns: for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}. Although convention theory was well studied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), these theories did not necessarily excluded each other, especially between modernization theory and feminist theory \cite{Hayf05}.

Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.  Identifying benefits of FGC practice is crucial to promote
sustainable change \cite{EffeVogt15}, and a community-based FGC perspective \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11,
KandNwak09, OdukAfol17} (to confirm) should also be recognized. This study takes both the dynamics of attitudes and intention of FGC
practices (beliefs of FGC benefits, and intention of cutting) into account at both a population and a community level to test whether
FGC is a result of social interactions of social agents through interpreting norms in expectance of rewards. \jd{This P. seems
insufficient to tie the theoretical explanation to our research questions. We should study Efferson's approach.} \cf{good point.
reframed and may still need more works.}

Modernization theory proposes that traditional social relationships and values would be eroded by modernization (e.g., with the improvement of wealth and education and emphasis of individual rights) (see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?).

@@

The main model is the “daughter” model, which analyzed associations of attitude (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms associating behavioral intention can be detected.  Additionally, we also decompose the model into two “structural” models:  “future” model to study women’s attitudes of FGC benefits and FGC continuance; and “future_daughter” model to examine the association of attitudes of FGC benefits, FGC continuance and intention of cutting daughters to understand how such positionss change the main model.

\jd{I guess this is also a good place to discuss our community variables?}

\cf{read \cite{Aske05, Brue05}}

@@

Only women with daughters to be considered for fgc were included in the main model (the daughter model) and the future-dughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
\jd{We need to know how DHS decided who to ask the question.}
\cf{Explain how we choose women}

\subsubsection{Measurements and Concepts}\label{measurements-and-concepts}
\cite{Rima08}*
\jd{Is this s. about us or not? Why is it in our Methods?} The main constructs analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} and applied in fgc studies (e.g., \{IloDarf18, PashPonn16}(more cites?). The theory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Here, the attitudes is constructed as women's attitudes of FGC benefits (see the list of FGC benefits at table XX in Appendix); perceived behavioral control as perception of gender awareness (i.e., women's attitudes towards domestic violence (see the list of attitudes towards domestic violence against women at table xx) and their social resources (education, and job?) (feminism and modernization?); and the perceived social pressures (subjective norms) as the community level of attitudes of FGC benefits and FGC prevalence (to reflect the convention norms of FGC under the convention theory). \cf{need comments!!!} \jd{Not sure what you're trying to do here. What do you mean by ``refer''? Seems loose.}

The main response variables in this study were woman's intention to cut their daughters in the daughter's FGC status model and the daughter-future model, and woman's attitude on whether they think FGC should be continued in the FGC future model.  The main predictors were attitudes of FGC benefits and woman's FGC status.  In order to test other theories mentioned above, we also included woman's gender awareness and other socio demogramic variables (see below).

The sociodemographic variables included age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, and residence (urban vs. rural) in addition to country.  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).

In order to address the significance of community impact on the practice of fgc, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cf{on a cluster leve, not national, right?} in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, OdukAfol17}).

\jd{How did the comments get so messed up? Can it not happen again?}
\cf{Cluster, which is usually larger than a village but small enough to be a social community, was used to represent a community level of impact \cite{Hayf05} (is Hayf05 correct or DHS method changes afterwards?}
\jd{Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.} \cf{Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.  But as J said, it is too hard! } %``explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior. `` \cite{Hayf05}
\cf{Bayesian model \cite{KandNwak09} ``Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level. Consequently, the spatial analysis will be affected by some random fluctuations.  Some of this random variation can be reduced through structured spatial effects because it includes neighboring observations in the analysis. However, it should be pointed out that such a spatial analysis should preferably be applied to census data, where the precision of the spatial analysis would be much higher." (p. 788)}

\cf{Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to perform the behavior (or not); and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.}

@@

\cf{Our response ARE categorical not binary; AND still need to explain why ethinicity is a random effect. AND media use was supposed to be incorporated as a random factor at the country level, based on the assumption that media content likely varied among countries.}

@@

-----stop reading -----

@@

Baseline socio-demographic and sample characteristics are shown in xxx.

Tables and figures including:
table of basic sociodemographic results
figure:  proportion of FGC daughters and FGC future
% figure:  plots of FGC benefits (This figure will be important. It tells us what women thinks about why FGC).
% figure: to put the first PCA of FGC believes of the 4 nations at the community level and maybe in one figure
% figure of significant variables on modernization and pile the findings of the 4 nations into one figure.
% a chart like figure 8-8D \cite{UNCI13}
% figure of FGC prevalence by age and country (see Hayf05)
% refer to https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/figure/F1/  \cite{SipsChen12} for a figure on intention of cutting daughter, mom's fgc status and their thoughts on fgc continuance.

Kenya 21% vs. 3% (2004-15 aged 15-49 women vs. 2010-15 aged 0-14 girls)
Mali 89% vs. ?
Nigeria 25% vs. 17%
Sierra Leone 90% vs. 13%
(We want DHS fgc rate and the rate from our samples)

\cf{findings on convention theory vs. modernization theory vs. gender theory}

\subsubsection{Basic Sociodemographic background}\label{Basic-Sociodemographic-background}
% adding how many ethnic groups in each nation based on DHS data.

\subsubsection{The FGC Future}\label{The-FGC-Future}

\subsubsection{Daughters' FGC Status}\label{Daughters'-FGC-Status}

\subsubsection{full model}\label{full-model}

% Kenya and Nigeria both were under %30 vs. Mali and Sierra Leon over %80.  Are they different in terms of norm and beahvior?  To discuss this in the discussion.

In the results of association of cutting daughter and mother's fgc status, the individual model and the community model were consistent; the effect of fgc prevalence among mothers, attitudes of fgc benefits and education were clear at the community level but not wealth, gender awareness and media consumption were not clear at the community level (meaning media use, gender awareness and education were less homogeneous?)

In the results of association of fgc future and mother's fgc status,

@@

--- by nations
---- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
1. comparison: \cite{Chia14, Hayf05}, and [http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya]
---- Mali: ``The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali. The populations of these countries share certain social and historical ties, which suggests that a strategy to eliminate FGM/C in one of these countries might be successful in others. FGM/C is practiced as part of the initiation into a secret society in Liberia and Sierra Leone. We should expect that the repercussions for mothers there who do not send their daughters to be initiated would be different than for mothers in nearby Mali or Guinea \cite{YodaWang13}

@@

>>>>

There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns: for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}. Both convention theory and gender approaches centre on values of how FGC associates with identity \cte{cites}.  Although convention theory was well studied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), gender perspective can shed lights on how women’s gender values intertwine with convention theory of FGC values \cite{cites}.   Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.

@@

Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}.  This study takes both the dynamics of beliefs of FGC benefits and of intention of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices l \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm).  We developed three models in this study.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.  Additionally, we also decompose the model into two “structural” models:  “future” model to study women’s beliefs of FGC benefits and FGC continuance; and “future_daughter” model to examine the association of beliefs of FGC benefits, FGC continuance and intention of cutting daughters to understand how such positions change the main model.

@@

Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the future-daughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
\cf{FGC module at https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}

\subsubsection{Measurements and Concepts}\label{measurements-and-concepts}
\cf{\cite{Rima08}}*

The main response variables were woman's intention to cut their daughters in the daughter model and the daughter-future model, and woman's attitude on whether FGC should be continued in the FGC future model.  The main predictors were beliefs of FGC benefits, woman's FGC status and attitudes of gender equality.  Other socio demographic variables were also included:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media and residence (urban vs. rural) in addition to country.  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).

In order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cf{on a cluster level, not national, right?} in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).  Cluster  was used to represent a community level of impact \cite{AligRen06, Hayf05}

\jdcmt{Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.} \cfcmt{Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.  But as J said, it is too hard! } %``explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior. `` \cite{Hayf05}
\cf{Bayesian model \cite{KandNwak09} ``Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level. Consequently, the spatial analysis will be affected by some random fluctuations.  Some of this random variation can be reduced through structured spatial effects because it includes neighboring observations in the analysis. However, it should be pointed out that such a spatial analysis should preferably be applied to census data, where the precision of the spatial analysis would be much higher." (p. 788)}
\cfcmt{Regarding FGC benefits modules, there were 9 questions.  Keya had all the 9, Mali and SL 7 (missing promiscuity and STD), NG 8, missing STD).  Should we drop STD since 3 out of 4 missed this variable?}

@@

\cfcmt{Our response ARE categorical not binary; AND still need to explain why ethnicity is a random effect. AND media use was supposed to be incorporated as a random factor at the country level, based on the assumption that media content likely varied among countries.}

@@

@@

Baseline socio-demographic and sample characteristics are shown in xxx.  The prevalence of FGC are \%, \%, \% and \% in Kenya, Mali, Nigeria and Sierra Leon accordingly.

Tables and figures to be included:
- table of basic sociodemographic results
- 3 figures of the results of the 3 models
- a figure of women’s FGC prevalence vs. their intention of cutting daughters vs. attitudes towards FGC continuity.  (ref to https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/, Fig 1)
% figure:  plots of FGC benefits (This figure will be important. It tells us what women thinks about why FGC).
% figure: to put the first PCA of FGC believes of the 4 nations at the community level and maybe in one figure
% a chart like figure 8-8D \cite{UNIC13}

@@

% “Many girls who are cut are daughters of women who oppose the practice” (\cite{UNIC13})
--- by nations
---- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
1. comparison: \cite{Chia14, Hayf05}, and [http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya]
---- Mali: ``The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali. The populations of these countries share certain social and historical ties, which suggests that a strategy to eliminate FGM/C in one of these countries might be successful in others. FGM/C is practiced as part of the initiation into a secret society in Liberia and Sierra Leone. We should expect that the repercussions for mothers there who do not send their daughters to be initiated would be different than for mothers in nearby Mali or Guinea \cite{YodaWang13}

@@

% Modernization theory proposes that traditional social relationships and values would be eroded by modernization (e.g., with the improvement of wealth and education and emphasis of individual rights) (see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?).
